Methods for Large Scale Learning to Rank

### 2014-04-06 report/Chapters/CrossBenchmarkComparison.tex
referenties van alle result-files verwerkt

AdaRank-\acs{MAP} &  &  & Linear Regression &  & \cite{Wang2012} \\ 

@@

BagBoo &  &  & MCP & \cite{Laporte2013} & \cite{Laporte2013} \\ 

@@

BoltzRank-Pair & \cite{Volkovs2009} & \cite{Volkovs2009} & OWPC & \cite{Usunier2009} & \cite{Usunier2009} \\ 

@@

CA &  & \cite{Busa-Fekete2013,Tan2013} & Q.D.\acs{KNN} &  &  \\ 

@@

Consistent-RankCosine &  & \cite{Tan2013} & RankAgg\acs{nDCG} &  &  \\ 

@@

FenchelRank & \cite{Lai2013} & \cite{Lai2013, Lai2013b,Laporte2013} & RankELM (pointwise) & \cite{Zong2013} & \cite{Zong2013} \\ 

@@

FP-Rank & \cite{Song2013} & \cite{Song2013} & Rank\acs{SVM} &  & \cite{Busa-Fekete2013, Freno2011} \\ 
FRank &  & \cite{Wang2012} & Rank\acs{SVM}-Primal &  &  \\ 

@@

Group\acs{CE} & \cite{Lin2011} & \cite{Lin2011} & RSRank &  &  \\ 

@@

IntervalRank & \cite{Moon2010} & \cite{Moon2010} & SmoothRank & \cite{Chapelle2010} & \cite{Chapelle2010} \\ 
\acs{IP}Rank & \cite{Wang2009b} & \cite{Torkestani2012} & SoftRank &  & \cite{Qin2010b} \\ 

@@

Kernel-\acs{PCA} RankBoost & \cite{Duh2008} & \cite{Duh2008} & SparseRank & \cite{Lai2013b} & \cite{Lai2013b} \\ 
KL-\acs{CRF} & \cite{Volkovs2011} &  & \acs{SVD}-RankBoost & \cite{Lin2009} & \cite{Lin2009} \\ 
LAC-MR-OR & \cite{Veloso2008} & \cite{Veloso2008} & \acs{SVM}$^{\acs{MAP}}$ &  & \cite{Wang2012} \\ 
LambdaMART & \cite{Burges2010} & \cite{Asadi2013a} & SwarmRank &  & \cite{Sato2013} \\ 
LambdaNeuralRank & \cite{Papini2012} & \cite{Papini2012} & TGRank &  &  \\ 
LambdaRank &  &  & TM & \cite{Zhou2008} & \cite{Zhou2008, Papini2012,Tan2013} \\ 

>>>>

AdaRank-\acs{MAP} &  &  & Linear Regression &  & \cite{Wang2012, Volkovs2011} \\ 

@@

BagBoo &  & \cite{Ganjisaffar2011c} & MCP & \cite{Laporte2013} & \cite{Laporte2013} \\ 

@@

BoltzRank-Pair & \cite{Volkovs2009} & \cite{Volkovs2009, Ganjisaffar2011c} & OWPC & \cite{Usunier2009} & \cite{Usunier2009} \\ 

@@

CA &  & \cite{Busa-Fekete2013,Tan2013} & Q.D.\acs{KNN} &  & \cite{Wang2013} \\ 

@@

Consistent-RankCosine &  & \cite{Tan2013} & RankAgg\acs{nDCG} & \cite{Wang2013} & \cite{Wang2013} \\ 

@@

FenchelRank & \cite{Lai2013} & \cite{Lai2013, Lai2013b, Laporte2013} & RankELM (pointwise) & \cite{Zong2013} & \cite{Zong2013} \\ 

@@

FP-Rank & \cite{Song2013} & \cite{Song2013} & Rank\acs{SVM} &  & \cite{Busa-Fekete2013, Freno2011, He2010} \\ 
FRank &  & \cite{Wang2012} & Rank\acs{SVM}-Primal &  & \cite{Lai2011} \\ 

@@

Group\acs{CE} & \cite{Lin2011} & \cite{Lin2011} & RSRank &  & \cite{Lai2013} \\ 

@@

IntervalRank & \cite{Moon2010} & \cite{Moon2010, Freno2011} & SmoothRank & \cite{Chapelle2010} & \cite{Chapelle2010} \\ 
\acs{IP}Rank & \cite{Wang2009b} & \cite{Wang2009b, Torkestani2012} & SoftRank &  & \cite{Qin2010b} \\ 

@@

Kernel-\acs{PCA} RankBoost & \cite{Duh2008} & \cite{Duh2008, Sato2013} & SparseRank & \cite{Lai2013b} & \cite{Lai2013b} \\ 
KL-\acs{CRF} & \cite{Volkovs2011} & \cite{Volkovs2011} & \acs{SVD}-RankBoost & \cite{Lin2009} & \cite{Lin2009} \\ 
LAC-MR-OR & \cite{Veloso2008} & \cite{Veloso2008} & \acs{SVM}$^{\acs{MAP}}$ &  & \cite{Wang2012, Xu2008, Niu2012} \\ 
LambdaMART & \cite{Burges2010} & \cite{Asadi2013a, Ganjisaffar2011c} & SwarmRank &  & \cite{Sato2013} \\ 
LambdaNeuralRank & \cite{Papini2012} & \cite{Papini2012} & TGRank &  & \cite{Lai2013} \\ 
LambdaRank &  &  & TM & \cite{Zhou2008} & \cite{Zhou2008, Papini2012, Tan2013} \\ 
